### 2012-11-25 paper.tex
converted all accuracy details to tables, still misplaced at the end of the paper

\usepackage{natbib}
% philipp: added for code listings
\usepackage{listings}
\usepackage{booktabs}
\bibliographystyle{plain}

@@

\paragraph{Raising the confidence factor}
Subsequently increasing the confidence factor, which result in less pruning, leads to a continuous worse quality. If we set the confidence factor to 0.5 we get the following outcome:
\begin{lstlisting}
=== Detailed Accuracy By Class ===
                TP Rate  FP Rate  Precision  Recall  F-Measure  Class
                0.632    0.071    0.738      0.632   0.681      >50K
                0.929    0.368    0.888      0.929   0.908      <=50K
Weighted Avg.   0.857    0.296    0.852      0.857   0.854      
\end{lstlisting}
.. for a confidence factor of 0.75 we get the following:
\begin{lstlisting}
=== Detailed Accuracy By Class ===
                TP Rate  FP Rate  Precision  Recall  F-Measure  Class
                0.655    0.094    0.689      0.655   0.672      >50K
                0.906    0.345    0.892      0.906   0.899      <=50K
Weighted Avg.   0.846    0.285    0.843      0.846   0.844     
\end{lstlisting}

@@

With default settings, a random forest achieves an accuracy as follows:
\begin{lstlisting}
=== Detailed Accuracy By Class ===
                TP Rate  FP Rate  Precision  Recall  F-Measure  Class
                0.615    0.108    0.644      0.615   0.629      >50K
                0.892    0.385    0.88       0.892   0.886      <=50K
Weighted Avg.   0.825    0.318    0.823      0.825   0.824     
\end{lstlisting}
which is surprisingly worse than the J48 algorithm.

@@

\begin{lstlisting}
=== Detailed Accuracy By Class ===
                TP Rate  FP Rate  Precision  Recall  F-Measure  Class
                0.606    0.064    0.749      0.606   0.67       >50K
                0.936    0.394    0.882      0.936   0.908      <=50K
Weighted Avg.   0.856    0.314    0.85       0.856   0.851     
\end{lstlisting}
We can push the accuracy even further, if we take more random trees, e.g. twenty:
\begin{lstlisting}
=== Detailed Accuracy By Class ===
                TP Rate  FP Rate  Precision  Recall  F-Measure  Class
                0.593    0.058    0.763      0.593   0.667      >50K
                0.942    0.407    0.879      0.942   0.909      <=50K
Weighted Avg.   0.858    0.323    0.851      0.858   0.851      
\end{lstlisting}

\paragraph{Number of features}
Increasing the number of features doesn't support the quality at all. The default number of features for this data set with 13 attributes is $ log_2(13) + 1 \approx 5 $. Choosing 6 attributes brinchoose gs us a precision of 84,9\% and with 10 randomly chosen features the precision falls back to 84.5\%. We can tease the most out of the random forest if we decrease the number of features a little. To be concise, we get the best achievable result, if we take only 3 randomly chosen
features.
\begin{lstlisting}
=== Detailed Accuracy By Class ===
                 TP Rate  FP Rate  Precision  Recall  F-Measure Class
                 0.577    0.052    0.779      0.577   0.663     >50K
                 0.948    0.423    0.876      0.948   0.911     <=50K
Weighted Avg.    0.859    0.333    0.853      0.859   0.851    
\end{lstlisting}
Which is a quite similar accuracy like the best of the J48 algorithm. 
\subsection{Support Vector Machine}

>>>>

\usepackage{natbib}
% philipp: added for code listings
\usepackage{listings}
\usepackage{booktabs}
\usepackage{morefloats}
\bibliographystyle{plain}

@@

\paragraph{Raising the confidence factor}
Subsequently increasing the confidence factor, which result in less pruning, leads to a continuous worse quality. If we set the confidence factor to 0.5 we get an outcome as shown in table \ref{tab:adult:dec:cf5} and if we set it to 0.75 the quality gets even worse as seen in \ref{tab:adult:dec:cf75}.
\begin{table*}[b]\centering
    \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
        \toprule 
        \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
              &  TP Rate & FP Rate & Precision & Recall & F-Measure & Class    \\  \midrule
              &  0.632   & 0.071   & 0.738     & 0.632  & 0.681     & >50K     \\ 
              &  0.929   & 0.368   & 0.888     & 0.929  & 0.908     & <=50K    \\ 
Weighted Avg. &  0.857   & 0.296   & 0.852     & 0.857  & 0.854     &          \\  \bottomrule
    \end{tabular*}
\caption{Decision Tree -- Confidence Factor of 0.5} 
\label{tab:adult:dec:cf5}
\end{table*}

\begin{table*}[b]\centering
    \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
        \toprule 
        \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
              &  TP Rate & FP Rate & Precision & Recall &  F-Measure &  Class  \\ \midrule        
              &  0.655   & 0.094   & 0.689     & 0.655  &  0.672     &  >50K   \\          
              &  0.906   & 0.345   & 0.892     & 0.906  &  0.899     &  <=50K  \\          
Weighted Avg. &  0.846   & 0.285   & 0.843     & 0.846  &  0.844     &         \\ \bottomrule          
    \end{tabular*}
\caption{Decision Tree -- Confidence Factor of 0.75} 
\label{tab:adult:dec:cf75}
\end{table*}

@@

With default settings, a random forest gains an accuracy on the census income data set that can be seen in table \ref{tab:adult:rand:default}:
\begin{table*}[b]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
      \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
                TP Rate  FP Rate  Precision  Recall  F-Measure  Class
                0.615    0.108    0.644      0.615   0.629      >50K
                0.892    0.385    0.88       0.892   0.886      <=50K
Weighted Avg.   0.825    0.318    0.823      0.825   0.824     
    \end{tabular*}
\caption{Random Forest -- Default Settings} 
\label{tab:adult:rand:default}
\end{table*}
which is surprisingly worse than the J48 algorithm.

@@

\begin{table*}[b]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
      \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
                TP Rate  FP Rate  Precision  Recall  F-Measure  Class
                0.606    0.064    0.749      0.606   0.67       >50K
                0.936    0.394    0.882      0.936   0.908      <=50K
Weighted Avg.   0.856    0.314    0.85       0.856   0.851     
    \end{tabular*}
\caption{Random Forest -- 7 Random Trees} 
\label{tab:adult:rand:7t}
\end{table*}
We can push the accuracy even further, if we take more random trees, e.g. twenty:
\begin{table*}[b]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
      \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
                & TP Rate  & FP Rate  & Precision &  Recall &  F-Measure  & Class  \\  \midrule          
                & 0.593    & 0.058    & 0.763     &  0.593  &  0.667      & >50K   \\     
                & 0.942    & 0.407    & 0.879     &  0.942  &  0.909      & <=50K  \\     
Weighted Avg.   & 0.858    & 0.323    & 0.851     &  0.858  &  0.851      &        \\  \bottomrule
    \end{tabular*}
\caption{Random Forest -- 20 Random Trees} 
\label{tab:adult:rand:20t}
\end{table*}

\paragraph{Number of features}
Increasing the number of features doesn't support the quality at all. The default number of features for this data set with 13 attributes is $ log_2(13) + 1 \approx 5 $. Choosing 6 attributes brinchoose gs us a precision of 84,9\% and with 10 randomly chosen features the precision falls back to 84.5\%. We can tease the most out of the random forest if we decrease the number of features a little. To be concise, we get the best achievable result, if we take only 3 randomly chosen
features.
\begin{table*}[b]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
      \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
               &  TP Rate & FP Rate & Precision & Recall & F-Measure & Class \\   \midrule
               &  0.577   & 0.052   & 0.779     & 0.577  & 0.663     & >50K  \\   
               &  0.948   & 0.423   & 0.876     & 0.948  & 0.911     & <=50K \\   
Weighted Avg.  &  0.859   & 0.333   & 0.853     & 0.859  & 0.851     &       \\   \bottomrule
    \end{tabular*}
\caption{Random Forest -- 3 Random Features} 
\label{tab:adult:rand:3f}
\end{table*}
Which is a quite similar accuracy like the best of the J48 algorithm. 
\subsection{Support Vector Machine}
